### 2024-11-29 parts/prelim.tex
knowledge correction

Let us introduce some compositional properties of
\kl{$\Rel$-polyregular functions} that will be used in this paper
to construct \kl{$\Rel$-polyregular functions}.
\begin{lemma}[{\cite[Theorem II.20]{CDTL23}}]
    \label{stability-polyregular:lemma}
    Let $d \geq 1$,
    $f,g \in \NPoly[d]$ (resp. $\ZPoly[d]$, $\NSF[d]$, $\ZSF[d]$),
    $L$ be a \kl{star-free language} over $\Sigma^*$,
    and $h \colon \Sigma^* \to \Gamma^*$ be a \kl{polyregular function}
    (resp. a \kl{star-free polyregular function}).
    Then, the following 
    are also in $\NPoly[d]$ (resp. $\ZPoly[d]$,
    $\NSF[d]$, $\ZSF[d]$):
    $f \circ h$,
    $f + g \defined w \mapsto f(w) + g(w)$,
    $f \times g \defined w \mapsto f(w) \times g(w)$,
    $\ind{L} \times f$.
    Furthermore, the above constructions preserve \kl{commutativity}.
\end{lemma}

>>>>

Let us introduce some compositional properties of
\kl{$\Rel$-polyregular functions} that will be used in this paper
to construct \kl{$\Rel$-polyregular functions}.
\begin{lemma}[{\cite[Theorem II.20]{CDTL23}}]
    \label{stability-polyregular:lemma}
    Let $d \geq 1$,
    $f,g \in \NPoly[d]$ (resp. $\ZPoly[d]$, $\NSF[d]$, $\ZSF[d]$),
    $L$ be a star-free language over $\Sigma^*$,
    and $h \colon \Sigma^* \to \Gamma^*$ be a \kl{polyregular function}
    (resp. a \kl{star-free polyregular function}).
    Then, the following 
    are also in $\NPoly[d]$ (resp. $\ZPoly[d]$,
    $\NSF[d]$, $\ZSF[d]$):
    $f \circ h$,
    $f + g \defined w \mapsto f(w) + g(w)$,
    $f \times g \defined w \mapsto f(w) \times g(w)$,
    $\ind{L} \times f$.
    Furthermore, the above constructions preserve \kl{commutativity}.
\end{lemma}
